Changes in Mobility and Site Occupation during the Late Pleistocene in Korea

### 2020-08-21 analysis/paper/paper.Rmd
adjust the inset plot location for site occupation

---
title: "Changes in Mobility and Site Occupation during the Late Pleistocene in Korea"
author:
  - Author Gayoung Park
  - Author Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  The Late Pleistocene saw the introduction of new lithic technologies to the Korean Peninsula, especially stemmed points and blades. We examined stone artifacts from 22 sites in Korea to investigate how the introduction of  new tools changed the way people used the landscape, and the way people used sites. We analyzed artifact density, retouch frequency, radiocarbon ages, site elevation, raw material types, and composition of the toolkit to test hypotheses about site use. The results show that the new technology enabled the occupation of marginal environments at higher elevations. We find no strong relationship between technology and ecological change. Instead, we assume that population dynamics might have had more impact on changes in stone artifact technology and hunter-gatherer foraging strategies. 
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
---

@@

```{r}
# site elevation

@@

library(cowplot)
ggdraw(elevation_sp_main_plot) +
  draw_plot(elevation_sp_sub_plot, 
            .475, .57, 
            .25, .32) 
```

@@

```{r}
#Volume and artefact counts to get density over time. 
kasv_tidy <- 
kasv %>% 
  t %>% 
  as_tibble() %>% 
  setNames(as.character(.[1,])) %>% 
  .[-1,] %>% 
  mutate_all(parse_number) %>% 
  mutate(artefact_density = total_artifacts / volume,
         sites = names(kasv)[-1]) %>% 
  left_join(mydata, by = c('sites' = 'site_name' )) %>% 
  mutate(has_sp = ifelse(is.na(SP.), "no", "yes"))

@@

size <-  8
Assemblage_info_retouch_density_ages_prop_main_plot <- 
ggplot(Assemblage_info_retouch_density_ages_prop,
       aes(artefact_density,
           prop_retouched
           )) +
  geom_point(aes(colour = date_age / 1000,
                 size = total_artifacts,
                 shape = has_sp)) +
 # geom_text_repel(aes(label = sites),
 #                 nudge_x = 0.075, 
 #                 nudge_y = -0.075,
 #                 size = 5) +
  geom_smooth(alpha = 0.2,
              method = "lm") +
  scale_y_log10(limits = c(0.001, 1),
                labels = scales::comma_format(accuracy = 0.001)) +
  scale_x_log10(limits = c(0.001, 10),
                labels = scales::comma_format(accuracy = 0.001)) +
  theme_minimal(base_size = 12) +
  scale_shape_discrete("Contains\nstemmed\npoints?") +
  scale_size("Total number\nof artifacts") +
  scale_color_viridis_c(name = "Age of\nassemblage (ka)") +
  xlab("Artifact volumetric density") +
  ylab("Proportion of retouched pieces") +
  annotate("text",
           x = 0.005,
           y = 0.7,
           label = "Curated",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 5,
           y = 0.01,
           label = "Expedient",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 0.03,
           y = 0.02,
           label = glue('r = {round(r_value, 3)}\nt({df_value}) =  {round(t_value, 3)}, p = {round(p_value, 3)}'),
           size = size - 2,
           colour = "grey50")

>>>>

---
title: "Changes in Mobility and Site Occupation during the Late Pleistocene in Korea"
author:
  - Author Gayoung Park
  - Author Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
bibliography: references.bib
csl: "../templates/journal-of-archaeological-science.csl" # Insert path for the bib-style
abstract: |
  The Late Pleistocene saw the introduction of new lithic technologies to the Korean Peninsula, especially stemmed points and blades. We examined stone artifacts from 22 sites in Korea to investigate how the introduction of  new tools changed the way people used the landscape, and the way people used sites. We analyzed artifact density, retouch frequency, radiocarbon ages, site elevation, raw material types, and composition of the toolkit to test hypotheses about site use. The results show that the new technology enabled the occupation of marginal environments at higher elevations. We find no strong relationship between technology and ecological change. Instead, we assume that population dynamics might have had more impact on changes in stone artifact technology and hunter-gatherer foraging strategies. 
keywords: |
  keyword 1; keyword 2; keyword 3
highlights: |
  These are the highlights. 
editor_options: 
  chunk_output_type: console
---

@@

```{r}
# site elevation
kasv_tidy <- 
kasv %>% 
  t %>% 
  as_tibble() %>% 
  setNames(as.character(.[1,])) %>% 
  .[-1,] %>% 
  mutate_all(parse_number) %>% 
  mutate(artefact_density = total_artifacts / volume,
         sites = names(kasv)[-1]) %>% 
  left_join(mydata, by = c('sites' = 'site_name' )) %>% 
  mutate(has_sp = ifelse(is.na(SP.), "no", "yes"))

@@

library(cowplot)
ggdraw(elevation_sp_main_plot) +
  draw_plot(elevation_sp_sub_plot, 
            .575, .60, 
            .25, .32) 
```

@@

```{r}
#Volume and artefact counts to get density over time.

@@

size <-  8
Assemblage_info_retouch_density_ages_prop_main_plot <- 
ggplot(Assemblage_info_retouch_density_ages_prop,
       aes(artefact_density,
           prop_retouched
           )) +
  geom_point(aes(colour = date_age / 1000,
                 size = total_artifacts,
                 shape = has_sp)) +
 # geom_text_repel(aes(label = sites),
 #                 nudge_x = 0.075, 
 #                 nudge_y = -0.075,
 #                 size = 5) +
  geom_smooth(alpha = 0.2,
              method = "lm") +
  scale_y_log10(limits = c(0.001, 1),
                labels = scales::comma_format(accuracy = 0.001)) +
  scale_x_log10(limits = c(0.001, 10),
                labels = scales::comma_format(accuracy = 0.001)) +
  theme_minimal(base_size = 12) +
  scale_shape_discrete("Contains\nstemmed\npoints?") +
  scale_size("Total number\nof artifacts") +
  scale_color_viridis_c(name = "Age of\nassemblage (ka)") +
  xlab("Artifact volumetric density") +
  ylab("Proportion of retouched pieces") +
  annotate("text",
           x = 0.005,
           y = 0.7,
           label = "Curated",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 5,
           y = 0.01,
           label = "Expedient",
           size = size -2,
           colour = "grey50") +
    annotate("text",
           x = 0.03,
           y = 0.02,
           label = glue('r = {round(r_value, 3)}\n, t({df_value}) =  {round(t_value, 3)}, p = {round(p_value, 3)}'),
           size = size - 2,
           colour = "grey50")
